\begin{thebibliography}{17}
  \addcontentsline{toc}{chapter}{Литература}
  \selectlanguage{english}

\bibitem{1}
  A. V. Aho, R. Sethi, and J. D. Ullman. \emph{Compilers: Principles, techniques, and tools.} Addison Wesley, Reading, Massachusetts, 1986.

\bibitem{2}
  J. L. Hennessy and D. A. Patterson. \emph{Computer architecture: A quantitative approach.} Morgan Kaufmann Publishers, Inc., San Mateo, California, 1990.

\bibitem{3}
  C. A. R. Hoare. Algorithm 64 quicksort. \emph{CACM}, 4(7):321, Jul 1961.

\bibitem{4}
  Adobe Systems Inc. \emph{PostScript language reference manual.} Addison Wesley, Reading, Massachusetts, 1985.

\bibitem{5}
  R. Jain. \emph{The art of Computer Systems Performance Analysis.}  John Wiley, Newyork, 1991.

\bibitem{6}
  B. W. Kernighan. PIC --- a language for typesetting graphics. \emph{Software~---~practice and experience,} 12(1):1–21, Jan 1982.

\bibitem{7}
  B. W. Kernighan and D. W. Ritchie. \emph{The C programming language~---~ANSI C.} Prentice Hall, Englewood Cliffs, New Jersey, second edition edition, 1988.

\bibitem{8}
  D. E. Knuth. \emph{The art of computer programming, volume 1: Fundamental algorithms.} Addison Wesley, Reading, Massachusetts, second edition, 1973.

\bibitem{9}
  L. C. Paulson. \emph{ML for the working programmer.} Cambridge Univ. Press, New York, 1991.

\bibitem{10}
  W. H. Press, B. P. Flannery, S. A. Tekolsky, and W. T. Vetterling. \emph{Numerical recipes in C --- The art of scientific computing.} Cambridge Univ. Press, Cambridge, England, 1993.

\bibitem{11}
  B. Schneier. \emph{Applied cryptography.} John Wiley \& Sons, Chichester, England, second edition edition, 1996.

\bibitem{12}
  R. Sedgewick. \emph{Algorithms.} Addison Wesley, Reading, Massachusetts, 1983.

\bibitem{13}
  E. H. Spafford. The internet worm program: an analysis. \emph{ACM Computer communication review,} 19(1):17–??, Jan 1989.

\bibitem{14}
  A. S. Tanenbaum. \emph{Structured computer organisation.} Prentice Hall, Englewood Cliffs, New Jersey, second edition, 1984.

\bibitem{15}
  J. D. Ullman. \emph{Elements of ML programming.} Prentice Hall, Englewood Cliffs, New Jersey, 1994.

\bibitem{16}
  A. Wikstr\"om. \emph{Functional programming using Standard ML.} Prentice Hall, London, England, 1987.

\bibitem{17}
  X-Consortium. \emph{X Window Manuals.} O’Reilly \& Associates, Inc., New York, 1990.

\end{thebibliography}
